SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-16 frontrunning/Latex/sections/paper.tex
[frontrunning] variants and minor fixes

In the first type of attack, a \textit{displacement attack}, it is not important to the adversary for Alice's function call to run after Mallory runs her function. Alice's can be orphaned or run with no meaningful effect. Examples of displacement include: Alice trying to register a domain name and Mallory registering it first~\cite{kalodner2015empirical}; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{breidenbach2018enter}; and Alice trying to submit a bid in an auction and Mallory copying it. In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first. We call this \textit{asymmetric displacement}. Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain. We call this \textit{bulk displacement}.

@@

@@

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}. %0x has also added an option to cancel all orders through a batch cancellation mechanism to mitigate this issue.

@@

\subsection{\textit{Status.im} ICO}
To deal with demand, ICOs cap sales in a variety of ways to mitigate front-running attacks. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, collecting close to 300,000 Ether. In order to prevent wealthy investors purchasing all the tokens and limit the amount of Ether deposited in each investment, they used a \textit{fair} token distribution method called \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors. They implemented multiple caps (ceilings) in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.

>>>>

In the first type of attack, a \textit{displacement attack}, it is not important to the adversary for Alice's function call to run after Mallory runs her function. Alice's can be orphaned or run with no meaningful effect. Examples of displacement include: Alice trying to register a domain name and Mallory registering it first~\cite{kalodner2015empirical}; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{breidenbach2018enter}; and Alice trying to submit a bid in an auction and Mallory copying it.

@@

Each of these attacks have two other variants, \textit{asymmetric} and \textit{bulk}. For example, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first. We call this \textit{asymmetric displacement}. Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain. We call this \textit{bulk displacement}.

@@

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the asymmetric displacement template and is illustrated in Figure~\ref{fig:MinerFrontrunning}. %0x has also added an option to cancel all orders through a batch cancellation mechanism to mitigate this issue.

@@

\subsection{\textit{Status.im} ICO}
To deal with demand, ICOs cap sales in a variety of ways to mitigate front-running attacks. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 16 hours, collecting close to 300,000 Ether. In order to prevent wealthy investors purchasing all the tokens and limit the amount of Ether deposited in each investment, they used a \textit{fair} token distribution method called \textit{Dynamic Ceiling} as an attempt to increase the opportunity for smaller investors. They implemented multiple caps (ceilings) in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.
